\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-08-31 paper.tex
update

\section{Checkpoint graph construction}

@@

\subsection{Checkpoints}\label{sec:security-checkpoint}
Let $q\in\real{nmT}$ be the MRS trajectory found in Chapter \ref{chapter:Multi-agent-ADMM} for $m$ sub-teams with time horizon $T=t_{e}$, with $q_{p}(t)$ be the reference trajectory waypoint for sub-team $p$ at time $t$. A checkpoint $v_i=(q_{i},t_{i})$ is a pair composed of a location $q_{i}=q_{p}(t_{i})$ and a time $t_{i}$ representing a co-observation between a sub-team $\cI_p$'s member and robots either from the same sub-team or different ones. For convenience, let $\cI_{v_{i}}$ represent the corresponding sub-team $v_{i}$ belongs to.

@@

\subsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
After locating checkpoints $\union_p V_p$ for all sub-teams, we can search for cross-trajectory edges to connected all checkpoints to trajectories. Cross-trajectory edges represents feasible paths between two references trajectories that allow robots to reach a different reference trajectories and perform co-observations with the corresponding sub-teams. Thus, at least one end of the edges must be a security checkpoint $v_{p} \in \union_p V_p$. Additionally, assuming that only one robot is sent at a time between trajectories, the cross-trajectory edges must satisfy the reachability constraints from Chapter~\ref{chapter:Reachability_Constraints} to ensure that no deviation to forbidden areas can be performed while switching trajectories.

@@

\subsection{In-trajectory edges}\label{sec:Graph-intro}

@@

\section{Co-observation planning problem}
In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network flow problem, and solve it using mixed-integer linear programs (MILP). We assume that there are always \emph{reference robot}s in each sub-team following the reference trajectory.  We want to plan the routes for additional \emph{cross-trajectory robots} to perform co-observation with the reference robots.

@@

 \begin{subequations} \label{eq:flow-coverage-problem}
     \begin{align}
        \min &\quad \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} &\label{eq:flow-cost}\\
        \subjectto & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij}, & \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1 & \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
        & f^k_{ij} \in \{0,1\} &  \forall (ij)\in E\label{eq:SingleFLowCapacity}
     \end{align}
 \end{subequations}

@@

\section{Co-observation performance}
Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{\cE} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{\cE}$, these flow will not increase the cost and will not have any impact on the solution.  
The trade-off between the number of surveillance robots used, and the overall security performance is a critical consideration in this case. Increasing the number of robots generally contributes to improved security by enabling more cross-trajectory co-observations. However, adding more robots can lead to diminishing returns, as the benefits gained from additional robots may be counterbalanced by increased complexity and coordination challenges. To capture this trade-off, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} allows us to fine-tune the balance between the number of robots employed and the desired task performance. By optimizing this parameter, we can strike a suitable equilibrium between security enhancement and operational efficiency.

@@

\section{Result and simulation}
In this section, we test the proposed method starting from the results in Figure \ref{fig:trajectories-more-constraint}, where three trajectories are provided for the map exploration task with no security related constraints (co-observation schedule and reachability). We use the same environment and dynamic setup, where we have a $10m\times10m$ task space, two forbidden regions (two rectangles in  \ref{fig:trajectories-more-constraint}) and robots with a max velocity of $0.5m/dt$.

@@

\section{Summary}
In this chapter, we provide a method to enhance the security of a multi-robot system without sacrificing the performance. This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories. We model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories. We have shown that the co-observation planning problem across different trajectories can be transformed into a multi flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.

>>>>

\subsection{Checkpoint graph construction}

@@

\subsubsection{Checkpoints}\label{sec:security-checkpoint}
Let $q\in\real{nmT}$ be the MRS trajectory found in Chapter \ref{chapter:Multi-agent-ADMM} for $m$ sub-teams with time horizon $T=t_{e}$, with $q_{p}(t)$ be the reference trajectory waypoint for sub-team $p$ at time $t$. A checkpoint $v_i=(q_{i},t_{i})$ is a pair composed of a location $q_{i}=q_{p}(t_{i})$ and a time $t_{i}$ representing a co-observation between a sub-team $\cI_p$'s member and robots either from the same sub-team or different ones. For convenience, let $\cI_{v_{i}}$ represent the corresponding sub-team $v_{i}$ belongs to.

@@

\subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
After locating checkpoints $\union_p V_p$ for all sub-teams, we can search for cross-trajectory edges to connected all checkpoints to trajectories. Cross-trajectory edges represents feasible paths between two references trajectories that allow robots to reach a different reference trajectories and perform co-observations with the corresponding sub-teams. Thus, at least one end of the edges must be a security checkpoint $v_{p} \in \union_p V_p$. Additionally, assuming that only one robot is sent at a time between trajectories, the cross-trajectory edges must satisfy the reachability constraints from Chapter~\ref{chapter:Reachability_Constraints} to ensure that no deviation to forbidden areas can be performed while switching trajectories.

@@

\subsubsection{In-trajectory edges}\label{sec:Graph-intro}

@@

\subsection{Co-observation planning problem}
In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network flow problem, and solve it using mixed-integer linear programs (MILP). We assume that there are always \emph{reference robot}s in each sub-team following the reference trajectory.  We want to plan the routes for additional \emph{cross-trajectory robots} to perform co-observation with the reference robots.

@@

 \begin{subequations} \label{eq:flow-coverage-problem}
     \begin{align}
        \min & \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
        s.t. & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij},  \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1, \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
        & f^k_{ij} \in \{0,1\} ,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
     \end{align}
 \end{subequations}

@@

\subsection{Co-observation performance}
Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{\cE} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{\cE}$, these flow will not increase the cost and will not have any impact on the solution.  
The trade-off between the number of surveillance robots used, and the overall security performance is a critical consideration in this case. Increasing the number of robots generally contributes to improved security by enabling more cross-trajectory co-observations. However, adding more robots can lead to diminishing returns, as the benefits gained from additional robots may be counterbalanced by increased complexity and coordination challenges. To capture this trade-off, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} allows us to fine-tune the balance between the number of robots employed and the desired task performance. By optimizing this parameter, we can strike a suitable equilibrium between security enhancement and operational efficiency.

@@

\subsection{Result and simulation}
In this section, we test the proposed method starting from the results in Figure \ref{fig:trajectories-more-constraint}, where three trajectories are provided for the map exploration task with no security related constraints (co-observation schedule and reachability). We use the same environment and dynamic setup, where we have a $10m\times10m$ task space, two forbidden regions (two rectangles in  \ref{fig:trajectories-more-constraint}) and robots with a max velocity of $0.5m/dt$.

@@

\section{Summary}
In this paper, we provide a method to enhance the security of a multi-robot system without sacrificing the performance. This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories. We model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories. We have shown that the co-observation planning problem across different trajectories can be transformed into a multi flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.
